The time since I accidentally started down the path to becoming a mathematician has been one of the most trying and rewarding parts of my life.
I owe a great debt of gratitude to Richard Foote, David Dummit, and John Voight for their outsized impact at the beginning of this journey at the University of Vermont eight years ago.
But for their outstanding classes, I do not believe I would be where I am now.
I would also like to thank my dear friends Paul Lessard and John willis, both of whom I was incredibly fortunate to meet as classmates at the University of Vermont, for helping make that experice, amongst a great many others, truly exceptional.

I am extremely grateful for the support and encouragement of the faculty at the University of South Carolina over the past six years, especially Andy Kustin and Frank Thorne for all of your wonderful courses and helpful advice.
I would also like to especially thank my advisor, Matt Ballard, for your very patient guidance, encouragement, and unwavering support.
%As if by magic, you have always seemed to know not only where I needed to go, but just the route I needed to take.
%Through your guidance I have learned and proven more than I thought myself capable.

I would also like to thank all of my friends and family for their support throughout this process.
I am very much grateful for the Fluid Dynamics \lq seminar,\rq\, through which I have met many of friends here at the University of South Carolina, and for my fellow captains who have helped navigate that wayward ship.

Finally, I would like to especially thank my beloved wife, Ann Clifton, for all your love, encouragement and support.
I, too, look forward to a lifetime of love, joy, and mathematics with you.
