\documentclass[12pt]{letter}

\usepackage[margin=1in]{geometry}
\openup 5pt
\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage{amsmath}
%\usepackage[all]{nowidow}

\signature{Blake Farman}
\address{
  306 Cattell St\\
  Floor 2\\
  Easton, PA 18042
}
\date{\today}

\def\school{Western Washington University}
\def\courses{linear or abstract algebra, and algebraic geometry}
\def\position{Assistant Professor position}
\def\posloc{MathJobs.org}

\def\diversityblurb{In all the courses that I teach, I feel that it is imperative to foster an inclusive environment.
  It is my firmly held belief that everyone should have equal access to education and, along this line, I believe that traditionally underrepresented groups should be embraced and encouraged, a sentiment shared by the community at Lafayette College.
  During my time here, I have had the opportunity to review literature regarding inclusivity in STEM, and to discuss these ideas and their implementation with fellow faculty members.
  I have also taken the opportunity to participate in biweekly teaching lunches within the mathematics department, where colleagues share their philosophies and methods for fostering an inclusive and effective teaching environment.
  As a direct result, I have incorporated examples from various disciplines which are relevant to students' lives, and implemented active learning techniques to reach a wide variety of learning styles.
  I look forward to the opportunity to continuing this work as my career progresses.}

\def\materials{the standard AMS cover sheet,
  a curriculum vitae,
  a research statement,
  and a teaching statement}
%a publication list,
%and a teaching portfolio}
%and an unofficial transcript}
\def\contacts{Tom Cassidy}

\def\numresrefs{three}
\def\numteachrefs{two}
\def\refs{Matthew Ballard,
  David Favero,
  and Colin Ingalls}
\def\teachingrefs{Matthew Boylan and Cliff Reiter}

\begin{document}
\begin{letter}{
    Math Department, BH 202, Western Washington University\\
    516 High St.\\
    Bellingham, WA 98225
  }
  \opening{Dear Members of the Search Committee,}


    My name is Blake Farman, and I am currently a Visiting Assistant Professor at Lafayette College.
  I received my Ph.D. from the University of South Carolina on May 12, 2018 under the direction of Matthew Ballard in the area of Noncommutative Projective Algebraic Geometry.
  I am writing to apply for the \position\ advertised on \posloc.

  My research lies at the intersection of Kontsevich and Artin-Zhang style noncommutative geometry, where I study the derived category of quasi-coherent sheaves on noncommutative projective schemes via the framework of differential graded categories.
  Fundamentally, the goal of this research is concerned with constructing tools that allow one to turn the lens of modern geometric intuition towards understanding the structure of noncommutative rings.
  This work draws from a wide range of subjects that fall largely within algebra, geometry, and category theory, and provides a broad perspective conducive to working with undergraduate students across a variety of interests.

  In particular, the perspective granted by my research preparation allows me to provide a meaningful dictionary between abstract algebraic concepts and tangible geometric examples, a skill that is clearly effective for communicating concepts to general mathematical audiences.
  I have made extensive use of this skill while teaching at the advanced undergraduate and graduate levels, where I have delivered guest lectures, seminars, and colloquia.
  However, it has proven itself especially invaluable in the introductory courses in which I have served as instructor of record, where I encounter many students whose interests lie outside of mathematics and for whom such imagery is most helpful in achieving a deeper conceptual understanding of the material.% beyond rote manipulation.

  Teaching at each of these levels presents its own set of challenges, which I have found rewarding, both as a graduate student and, especially, in my current position at Lafayette College.
  I am eager to have the opportunity to teach advanced courses such as \courses, in addition to conducting research, both along the program outlined in my research statement, as well as on related topics accessible to undergraduate students.
  I believe that \school\ will provide the ideal environment to achieve this goal, and, moreover, I believe that my experience at Lafayette has prepared me to excel in a student-centered setting.%small liberal arts setting.
  
%  In particular, the perspective granted by my research preparation allows me to provide a meaningful dictionary between abstract algebraic concepts and tangible geometric examples, a skill that is clearly effective for communicating concepts to mathematical audiences, such as lectures aimed at advanced undergraduate/early graduate audiences, seminars, and colloquium talks.
  %However, it has proven itself especially invaluable in introductory courses, where I encounter many students whose interests lie outside of mathematics and for whom such imagery most helps to achieve a deeper conceptual understanding of the material.% beyond rote manipulation.

  
  
  %As an instructor, I am always excited to share this and any other insight I can with students.
  %Indeed, I take great joy especially in seeing the proverbial 'light bulb' turn on in a student's mind.
  
    %As an instructor, I have a deep appreciation for the beauty and power of mathematics that I am always excited to share with students.
  %Additionally, I believe I am not only excited, but well situated, to supervise research projects in algebra or geometry broadly.

%  My research lies at the intersection of Kontsevich and Artin-Zhang style noncommutative geometry, where I study the derived category of quasi-coherent sheaves on the noncommutative projective schemes of Artin-Zhang via the framework of differential graded categories.
  %My dissertation provides a noncommutative definition of integral transform and proves, under appropriate cohomological assumptions, that to any equivalence between derived categories of quasi-coherent sheaves one may associate an integral transform.
  %In the commutative situation, the analogous result is due to Orlov (and To\"{e}n and Lunts in more generality), and forms a corner stone for our understanding of derived categories in algebraic geometry.

\diversityblurb
  
  With my application, I include \materials.
  I have also arranged for \numresrefs\  letters of recommendation regarding my research from \refs, and \numteachrefs\ letters of recommendation regarding my teaching from \teachingrefs.
  %I also include \numresrefs\ letters of recommendation regarding my research from \refs.

  %\MSPRF
  
  Please let me know if there is anything else I can provide.
  Thank you in advance for your time and consideration.
  \closing{Sincerely,}
  \encl{
    Curriculum Vitae\\
    Research Statement\\
    Teaching Statement\\
    %Publication List\\
    %Unofficial Transcript
    %Teaching Portfolio
  }
\end{letter}
\end{document}
