\documentclass[dissertation.tex]{subfiles}
\begin{document}
\begin{defn}
  Let $\CC$ be a category.
  \begin{itemize}
  \item
    We say a subcategory $\CC^\prime$ of $\CC$ is {\it full} if 
    $\Hom{\CC^\prime}{X,Y} = \Hom{\CC}{X,Y}$
    for all objects $X,Y$ of $\CC^\prime$.
  \item
    We say a full subcategory $\CC^\prime$ of $\CC$ is {\it strictly full} if whenever $X \rightarrow Y$ is an isomorphism with $X$ an object of $\CC^\prime$, then $Y$ is an object of $\CC^\prime$.
  \end{itemize}
\end{defn}

\begin{defn}
  Let $\CC$ be a category, and let $f : X \to Y$ be a morphism of $\CC$.
  \begin{itemize}
    \item
      If $f$ is a monomorphism, we say that $f$ is {\it normal} if it is the kernel of some morphism $Y \rightarrow Z$.
    \item
      If $f$ is an epimorphism, we say that $f$ is {\it conormal} if $f$ is the cokernel of some morphism $Z \rightarrow X$.
    \item
      If every monomorphism of $\CC$ is normal, then we say that $\CC$ is {\it normal}.
    \item
      If every epimorphism of $\CC$ is conormal, then we say that $\CC$ is {\it conormal}.
    \item
      If $\CC$ is both normal and conormal, then we say that $\CC$ is {\it binormal}.
  \end{itemize}
  
\end{defn}

\begin{defn}
  Let $\CC$ be a category.
  \begin{itemize}
  \item
    We say that $\CC$ is {\it $\Ab$-enriched} if for every pair of objects $X$ and $Y$ of $\CC$, $\Hom{\CC}{X,Y}$ is an abelian group and composition 
    $$\Hom{\CC}{X,Y} \times \Hom{\CC}{Y,Z} \rightarrow \Hom{\CC}{X,Z}$$
    is $\Z$-bilinear.
  \item
    We say that an $\Ab$-enriched category, $\CC$, is {\it pre-additive} if $\CC$ has a zero object.
  \item
    We say that a pre-additive category, $\CC$, is {\it additive} if $\CC$ admits all binary products or coproducts.
    \begin{rmk}
      Note that in this case, it is straightforward to show that any finite product is also a coproduct and vise-versa.
    \end{rmk}
  \item
    We say that an additive category, $\CC$, is {\it abelian} if $\CC$ is binormal.
  \end{itemize}
\end{defn}

\begin{defn}
  Let $\CC$ and $\D$ be additive categories.
  A functor $\mathscr{F} \colon \CC \rightarrow \D$ is called an {\it additive functor} if 
  \begin{enumerate}
  \item
    $\mathscr{F}(0) \cong 0$, and
  \item
    For any two objects $X$ and $Y$ of $\CC$,
    $$F(X \oplus Y) \cong F(X) \oplus F(Y).$$
  \end{enumerate}
\end{defn}
\end{document}
