% LaTeX resume using res.cls
\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\pdfpagewidth 8.5in
\pdfpageheight 11in
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}
\noindent\textbf{\large{Blake Alexander Farman}} \hfill \today\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\section*{Contact Information}
\begin{minipage}{1.3in}
  2807 Holt Dr.\\
  Columbia, SC 29205
\end{minipage}
\hfill
\begin{minipage}{2.15in}
  farmanb@math.sc.edu\\
  %+1 802 282 8205\\
  \hyperref[http://people.math.sc.edu/farmanb]{http://people.math.sc.edu/farmanb}
\end{minipage}

%  \section*{Objective}
%  I endeavour to find a position in which I have ample
%  opportunity to apply my knowledge of both computer science and mathematics.
  
  \section*{Education} 
  \textsl{Doctor of Philosophy,} Mathematics \hfill May 12, 2018\\
  University of South Carolina, Columbia, SC\\
  Dissertation Title: Geometry of derived categories on noncommutative projective schemes\\
  Advisor: Matthew R. Ballard\\
  
  \noindent
  \textsl{Master of Science,} Mathematics \hfill May 22, 2011\\
  University of Vermont, Burlington, VT\\
  Concentration: Abstract Algebra/Algebraic Number Theory\\
  %Minor Concentration: Algebraic Number Theory\\
  
  \noindent\textsl{Bachelor of Science,} Computer Science \hfill May 16, 2009\\
  Rensselaer Polytechnic Institute, Troy, NY\\
  Minors: Applied Mathematics and French

  \section*{Papers/Preprints}
  with Matthew Ballard.  \textsl{Kernels for Noncommutative Projective Schemes.} 
  arXiv:1709.06470 \hfill Submitted
  
  \section*{Employment}
  \textsl{Graduate Teaching Assistant} \hfill August 2012 - May 2018 \\
  University of South Carolina, Columbia, SC
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item
    Taught undergraduate level mathematics courses ranging from basic college algebra to calculus II while working towards a Ph.D in Mathematics.
  \item 
    Helped run a mathematics department sponsored tutoring center for undergraduates.
  \end{itemize}

  \noindent\textsl{Associate} \hfill August 2011 - August 2012\\
  Princeton Consultants, Inc, Princeton, NJ
  \begin{itemize}\itemsep -2pt
  \item
    Assisted in back end design of a web based planning utility for intermodal logistics.
  \item
    Java development, build management, scripting, and other back end development.
  \end{itemize}
  
  \noindent\textsl{Graduate Teaching Assistant} \hfill August 2009 - May 2011 \\
  University of Vermont, Burlington, VT
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item
    Taught undergraduate level introductory calculus and discrete mathematics courses while working towards an M.S. in Mathematics.
  \item 
    Helped run a mathematics department sponsored Help Session for undergraduates.
  \end{itemize}

  \noindent\textsl{Undergraduate Research/Teaching Assistant} \hfill May 2008 - May 2009 \\
  Rensselaer Polytechnic Institute, Troy, NY
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item Assisted Professor Jeffrey C. Trinkle and his student, Steven Berard, with development of the Qt interface for the daVinci Code (DVC) physical simulator.
  \item Served as Teaching Assistant for Professor Trinkle's Robotics Course, which used DVC.
    Responsibilities included teaching students how to use the software and designing/grading homework assignments that used DVC.
  \end{itemize}

  %\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
  %Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
  %charity event to benefit the Troy Boys Club. Over 
  %250 people participated each year. 
%  \section*{Other Experience}             
%  {\it Mountain Ambassador} \hfill Winters 2004-2008\\
%  Killington, Ltd., Killington, VT \\
%  The Killington Ambassador Program is an on-slope volunteer program designed to improve the experience of guests by providing local knowledge, information, directions, safety tips, and just about any other help a guest might need.

%  \section*{Honors}
%  Rensselaer Medalist\\
%  Four year, \$60,000 merit scholarship to Rensselaer Polytechnic Institute.
  
%  \section{HOBBIES}
%  Snowboarding, Hiking, Biking, Reading

\end{document}







