\documentclass[teaching.portfolio.tex]{subfiles}
\begin{document}
\subsection{Numerical}
Collected in the following table is an average of the instructor evaluations for the courses taught at the University of South Carolina, on a scale from 0 to 5.

\begin{tabular}{|c|c|c|}
  \hline
  \textbf{Semester} & \textbf{Course} & \textbf{Evaluation}\\
  \hline
  Fall 2012 & Calculus II (Sect. 009) & 4.2\\
  & Calculus II (Sect.010) & 4.26\\
  \hline
  Spring 2013 & Calculus I (Sect. 007) & 3.66\\
  & Calculus I (Sect. 008) & 4.21\\
  \hline
  Summer 2013 & Basic College Mathematics & 4.43\\
  \hline
  Fall 2013 & Brief Precalculus Mathematics (Sect. E1B) & 4.02\\
  & Brief Precalculus Mathematics (Sect. E2B) & 3.77\\
  \hline
  Spring 2014 & Finite Mathematics & 4.04\\
  \hline
  Summer 2014 & Calculus II & 4.65\\
  \hline
  Fall 2014 & Precalculus & 4.41 \\
  \hline
  Spring 2015 & Basic College Mathematics & 4.21\\
  \hline
  Fall 2015 & Brief Precalculus Mathematics (Sect E1B) & 4.68\\
  & Brief Precalculus Mathematics (Sect E2B) & 4.45\\
  \hline
  Spring 2016 & Finite Mathematics & 4.51\\
  \hline
  Fall 2016 & Brief Precalculus Mathematics (Sect E1B) & 4.53\\
  & Brief Precalculus Mathematics (Sect E2B) & 4.73\\
  \hline
  Spring 2017 & Calculus for Business Administration and Social Sciences & 4.07\\
  \hline
\end{tabular}
\subsection{Student Feedback}
On each of the evaluations is a free response section where students can provide feedback in their own words.
The following are a few of the responses received over the past six years.\\

\begin{quotation}
  ``\textit{He was always willing to help out before, during, \& after class.  He knew the subject was difficult and wanted us to better our understanding}'' -- Student, Calculus II, Fall 2012 (University of South Carolina)
\end{quotation}

\begin{quotation}
  ``\textit{Very patient, makes sure everyone understands.}'' -- Student, Precalculus, Fall 2014 (University of South Carolina)
\end{quotation}

\begin{quotation}
  ``\textit{Very nice and approachable.  He took time to make sure problems were dealt with and that everyone understood the material.}'' -- Student, Basic College Mathematics, Spring 2015 (University of South Carolina)
\end{quotation}

\begin{quotation}
  ``\textit{He made the material very easy to understand.  Easily one of the best math teachers I've ever had}'' -- Student, Basic College Mathematics, Spring 2015 (University of South Carolina)
\end{quotation}

\begin{quotation}
  ``\textit{This class was AWESOME!  It was best part of my day.  Nothing is as exciting as coming to this class to learn about math.}'' -- Student, Finite Mathematics, Spring 2016 (University of South Carolina)
\end{quotation}

\begin{quotation}
  ``\textit{He was very willing to help and understood the subject, but sometimes explained it in a far too advanced way.}'' -- Student, Calculus for Business Administration and Social Sciences, Spring 2017 (University of South Carolina)
\end{quotation}

\end{document}

