% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\pdfpagewidth 8.5in
\pdfpageheight 11in
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}
\name{Blake A. Farman}
% \address used twice to have two lines of address
\address{13B Franklin Street, Winooski, VT 05404}
\address{(802) 282-8205}

\begin{resume}
  
%  \section{OBJECTIVE}
%  I endeavour to find a position in which I have ample
%  opportunity to apply my knowledge of both computer science and mathematics.
  
  \section{EDUCATION} {\sl Master of Science,} Mathematics\\
  % \sl will be bold italic in New Century Schoolbook (or
  % any postscript font) and just slanted in
  % Computer Modern (default) font
  University of Vermont, Burlington, VT, 
  received May 2011, 
  GPA 3.74/4.0\\
  Concentration: Abstract Algebra\\
  Minor: Algebraic Number Theory

  {\sl Bachelor of Science,} Computer Science \\
  % \sl will be bold italic in New Century Schoolbook (or
  % any postscript font) and just slanted in
  % Computer Modern (default) font
  Rensselaer Polytechnic Institute, Troy, NY, 
  received May 2009,
  GPA 3.13/4.0\\
  Concentration: Computer Science \\
  Minors: Mathematics, French\\

  \section{RELATED\\EXPERIENCE} 
  {\sl Graduate Teaching Fellow} \hfill May 2010 - Present \\
  University of Vermont, Burlington, VT\\
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item
    Taught undergraduate level introductory calculus and discrete mathematics courses while working towards an M.S. degree.
  \item 
    Helped run a math department sponsored Help Session for undergraduates.
  \end{itemize}

  {\sl Undergraduate Research/Teaching Assistant} \hfill May 2008 - May 2009 \\
  Rensselaer Polytechnic Institute, Troy, NY\\
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item Assisted Professor Jeffrey C. Trinkle \& Steven Berard with development of the Qt interface for the daVinci Code (DVC) physical simulator\\ (http://www.robotics.cs.rpi.edu/dvc).
  \item Served as Teaching Assistant for Professor Trinkle's Robotics Course, which used DVC.
    Responsibilities included teaching students how to use the software and designing/grading homework assignments that used DVC.
  \end{itemize}

  {\sl Intern} \hfill            Summers 2005-2007 \\
  Vermont Electric Power Company (VELCO), Rutland, VT \\
  \begin{itemize}  \itemsep -2pt %reduce space between items
  \item{2007} Assisted VELCO's Information Systems group with development of stand alone and Microsoft SharePoint composite software for dynamic tracking of network hosts and a Virtual Help Desk solution.
  \item{2006}
    Assisted VELCO's System Protection group with software maintenance and development including preparation for installing software for automatic retrieval of information from Digital Fault Recorders and Relays.
  \item{2005}
    Assisted the VELCO Information Systems department with network maintenance, PC preparation, operating systems \& software installation and maintenance.
  \end{itemize} 

  %\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
  %Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
  %charity event to benefit the Troy Boys Club. Over 
  %250 people participated each year. 
  \section{OTHER\\ EXPERIENCE}             
  {\it Mountain Ambassador} \hfill Winters 2004-2008\\
  Killington, Ltd., Killington, VT \\
  The Killington Ambassador Program is an on-slope volunteer program designed to improve the experience of guests by providing local knowledge, information, directions, safety tips, and just about any other help a guest might need.

  \section{HONORS}
  Rensselaer Medalist
  
%  \section{HOBBIES}
%  Snowboarding, Hiking, Biking, Reading

\end{resume}
\end{document}







