% LaTeX resume using res.cls
\documentclass[margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Blake A. Farman}
% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% \address used twice to have two lines of address
\address{{\bf Present Address}\\BARH C308\\1999 Burdett Ave\\Troy, NY 12180\\(802) 282-8205}
\address{{\bf Permanent Address}\\PO Box 1331\\Castleton, VT 05735\\farmab@rpi.edu}
%\address{}
%\address{(802) 282-8205}

\begin{resume}
\section{\sl  Objective}  % with postscript font \sl produces bold italic
%                           with default font (CM) \sl produces slanted type
Short term, I am looking to be employed in a challenging software development environment where I can make ample use of both my computer science \& math skills.  Long term, I am looking to pursue a Ph.D in either applied mathematics or computer science leading to a career in research and possibly teaching at the collegiate level.

\section{\sl  Education}
\begin{ncolumn}{2}
{\it Rensselaer Polytec. Institute, Troy, NY} &  August 2005 - Present
\end{ncolumn}\\
Persuing B.S. Computer Science, with minors in Mathematics and French, GPA 3.1/4.0, expected May 2009

\begin{ncolumn}{2}
{\it Rutland Senior High School, Rutland, VT} & August 2001 - June 2005
\end{ncolumn}\\
Graduated with 3.6 GPA

\section{\sl  Related Experience}
\begin{ncolumn}{2}
{\it Undergraduate Research Experience} & May 2008 - August 2008
\end{ncolumn}\\
Rensselaer Polytechnic Institute, Troy, NY\\
Assisted Professor Jeffrey C. Trinkle \& Steven Berard  with development of the daVinci Code physical simulator (http://www.robotics.cs.rpi.edu/dvc).

\begin{ncolumn}{2}
{\it Software Development Intern} & June 2007 - August 2007
\end{ncolumn}\\  
Vermont Electric Power Company (VELCO), Rutland, VT \\
Assisted VELCO's Information Systems group with development of stand alone and Microsoft SharePoint composite software for dynamic tracking of network hosts and a Virtual Help Desk solution.

\begin{ncolumn}{2} 
{\it System Protection Intern} &  May 2006 - August 2006
\end{ncolumn}\\
Vermont Electric Power Company (VELCO), Rutland, VT\\
Assisted VELCO's System Protection group with software maintenance and development including prepration for installing software for automatic retrieval of information from Digital Fault Recorders and Relays.

\begin{ncolumn}{2}
{\it Information Systems Intern}  &   June 2005 - August 2005 
\end{ncolumn}\\
Vermont Electric Power Company (VELCO), Rutland, VT\\
Assisted the VELCO IS department with network maintenance, PC preparation, operating systems \& software installation and maintenance.

\section{\sl  Other Experience}
\begin{ncolumn}{2}
{\it Mountain Ambassador} & November 2004 - May 2008
\end{ncolumn}\\
Killington Ltd., Killington, Vermont\\
The Killington Ambassador Program is an on-slope volunteer program designed to improve the experience of guests by providing local knowledge, information, directions, safety tips, and just about any other help a guest might need.

\section{\sl  Honors}
Rensselaer Medalist

\end{resume}
\end{document}
