% LaTeX resume using res.cls
\documentclass[line,overlapped]{res} 
\pdfpagewidth 8.5in
\pdfpageheight 11in
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}
\name{Blake A. Farman}
% \address used twice to have two lines of address
\address{2420 Monroe Street}
\address{Columbia, SC 29205}

\begin{resume}
  
  %  \section{OBJECTIVE}
  %  I endeavour to find a position in which I have ample
  %  opportunity to apply my knowledge of both computer science and mathematics.
  
  \section{EDUCATION} 
          {\sl Doctor of Philosophy,} Mathematics \hfill August 2012 - Present\\
          % \sl will be bold italic in New Century Schoolbook (or
          % any postscript font) and just slanted in
          % Computer Modern (default) font
          University of South Carolina, Columbia, SC

          {\sl Master of Science,} Mathematics \hfill May 2011\\
          % \sl will be bold italic in New Century Schoolbook (or
          % any postscript font) and just slanted in
          % Computer Modern (default) font
          University of Vermont, Burlington, VT\\
          Major Concentration: Abstract Algebra\\
          Minor Concentration: Algebraic Number Theory.

          {\sl Bachelor of Science,} Computer Science \hfill May 2009\\
          % \sl will be bold italic in New Century Schoolbook (or
          % any postscript font) and just slanted in
          % Computer Modern (default) font
          Rensselaer Polytechnic Institute, Troy, NY\\
          Minors: Applied Mathematics and French

          \section{EMPLOYMENT}
                  {\sl Graduate Teaching Assistant} \hfill August 2012 - Present \\
                  University of South Carolina, Columbia, SC
                  \begin{itemize}  \itemsep -2pt % reduce space between items
                  \item
                    Teach undergraduate level mathematics courses while working towards a Ph.D in Mathematics.
                  \item 
                    Help run a math department sponsored Help Session for undergraduates.
                  \end{itemize}
                  
                  {\sl Graduate Teaching Assistant} \hfill August 2009 - May 2011 \\
                  University of Vermont, Burlington, VT
                  \begin{itemize}  \itemsep -2pt % reduce space between items
                  \item
                    Taught undergraduate level introductory calculus and discrete mathematics courses while working towards an M.S. in Mathematics.
                  \item 
                    Helped run a math department sponsored Help Session for undergraduates.
                  \end{itemize}

                  {\sl Undergraduate Research/Teaching Assistant} \hfill May 2008 - May 2009 \\
                  Rensselaer Polytechnic Institute, Troy, NY
                  \begin{itemize}  \itemsep -2pt % reduce space between items
                  \item Assisted Professor Jeffrey C. Trinkle \& Steven Berard with development of the Qt interface for the daVinci Code (DVC) physical simulator\\ (http://www.robotics.cs.rpi.edu/dvc).
                  \item Served as Teaching Assistant for Professor Trinkle's Robotics Course, which used DVC.
                    Responsibilities included teaching students how to use the software and designing/grading homework assignments that used DVC.
                  \end{itemize}

                  \section{CONFERECES ATTENDED}
                          {\sl Georgia Algebraic Geometry Symposium} \hfill October 2015\\
                          Emory University, Atlanta, GA

                          {\sl AMS Summer Institute in Algebraic Geometry} \hfill July 27 - 31, 2015\\
                          University of Utah, Salt Lake City, UT

                          {\sl Georgia Algebraic Geometry Symposium} \hfill October 2014\\
                          University of Georgia, Athens, GA

                          {\sl Arizona Winter School} \hfill March 2014\\
                          University of Arizona, Tucson, AZ

                          {\sl Palmetto Area Number Theory Series (PANTS) XXI} \hfill December 2013\\
                          Clemson University, Clemson, SC

                          {\sl Palmetto Area Number Theory Series (PANTS) XX} \hfill September 2013\\
                          Davidson College, Davidson, NC

                          {\sl Algebraic Geometry Northeastern Series (AGNES)} \hfill April 2013\\
                          Yale University, New Haven, CT

                          {\sl AMS Spring Western Sectional Meeting} \hfill April 2013\\
                          University of Colorado, Boulder, CO

                          {\sl Palmetto Area Number Theory Series (PANTS) XIX} \hfill December 2012\\
                          University of South Carolina, Columbia, SC

                          {\sl Palmetto Area Number Theory Series (PANTS) XVIII} \hfill September 2012\\
                          Wake Forest University, Winston-Salem, NC

                          \section{TEACHING EXPERIENCE}
                          {\bf University of South Carolina}, Columbia, SC

                          {\sl Math 116 - Brief Precalculus Mathematics} \hfill Fall 2015\\
                          Instructor of Record.

                          {\sl Math 111 - Basic College Mathematics} \hfill Spring 2015\\
                          Instructor of Record.

                          {\sl Math 115 - Precalculus Mathematics} \hfill Fall 2014\\
                          Instructor of Record.

                          {\sl Math 142 - Calculus II} \hfill July 2014\\
                          Instructor of Record.

                          {\sl Math 170 - Finite Mathematics} \hfill Spring 2014\\
                          Instructor of Record.

                          {\sl Math 116 - Brief Precalculus Mathematics} \hfill Fall 2013\\
                          Instructor of Record.
                          

                          {\sl Math 111 - Basic College Mathematics} \hfill May - June 2013\\
                          Instructor of Record.

                          {\sl Math 141 - Calculus I} \hfill Spring 2013\\
                          Teaching Assistant.

                          {\sl Math 142 - Calculus II} \hfill Fall 2012\\
                          Teaching Assistant.

                          {\bf University of Vermont,} Burlington, VT

                          {\sl Math 019 - Fundamentals of Calculus I} \hfill Fall 2011\\
                          Instructor of Record.

                          {\sl Math 017 - Applications of Finite Math} \hfill Summer 2010\\
                          Instructor of Record.

                          \newpage
                          
                          {\sl Math 017 - Applications of Finite Math} \hfill Spring 2010\\
                          Instructor of Record.

                          {\sl Math 017 - Applications of Finite Math} \hfill Fall 2009\\
                          Instructor of Record.
                          \section{SERVICE}

                          {\sl University of South Carolina High School Math Contest Proctor} \hfill January 2015\\
                          {\sl University of South Carolina High School Math Contest Proctor} \hfill February 2014\\
                          {\sl University of South Carolina High School Math Contest Proctor} \hfill January 2013
                          
                          
                          \section{NON-ACADEMIC\\EMPLOYMENT}             
                                  {\sl Associate} \hfill August 2011 - August 2012\\
                                  Princeton Consultants, Inc, Princeton, NJ\\
                                  Information Technology consultant.

                                  {\it Mountain Ambassador} \hfill Winters 2004-2008\\
                                  Killington, Ltd., Killington, VT \\
                                  The Killington Ambassador Program is an on-slope volunteer program
                                  designed to improve the experience of guests by providing local knowledge, 
                                  information, directions, safety tips, and just about any other help a guest might need.

%                                  {\sl Intern} \hfill            Summers 2005-2007 \\
%
%                                  Vermont Electric Power Company (VELCO), Rutland, VT \\
%                                  \begin{itemize}  \itemsep -2pt %reduce space between items
%                                  \item{2007} Assisted VELCO's Information Systems group with development of stand alone and Microsoft SharePoint composite software for dynamic tracking of network hosts and a Virtual Help Desk solution.
%                                  \item{2006}
%                                    Assisted VELCO's System Protection group with software maintenance and development including preparation for installing software for automatic retrieval of information from Digital Fault Recorders and Relays.
%                                  \item{2005}
%                                    Assisted the VELCO Information Systems department with network maintenance, PC preparation, operating systems \& software installation and maintenance.
%                                  \end{itemize} 
                                  
                                  \section{HONORS}
                                  Rensselaer Medalist
                                  
                                  %  \section{HOBBIES}
                                  %  Snowboarding, Hiking, Biking, Reading

\end{resume}
\end{document}







