\documentclass{letter}
\signature{Blake Farman}
\address{13B Franklin Street\\Winooski, VT 05404}
\begin{document}

\begin{letter}{Denver Summit Schools}
  \opening{To whom it may concern:}

  I am writing to you with regard to the Mathematics Tutor Fellowship posting on Monster.  
  I will be graduating this May from the University of Vermont with a master of science degree in mathematics and I am currently seeking employment in the field of education.  
  I am very interested in this position and I believe my skills and background will fit your needs.

  I am a passionate and devoted student of mathematics.  
  Indeed, I hold the field in high esteem and I aspire to impart my appreciation of its inherent beauty.  
  It is in part this aspiration that led me choose to attend the University of Vermont, where I was afforded the opportunity to independently teach a total of five undergraduate level mathematics courses in introductory discrete mathematics and calculus.  
  During this time I have found teaching to be an extremely rewarding endeavour and one which matches in equal measure the great fondness I hold for my own studies.  
  I have acquired significant experience in preparing and delivering lectures, crafting exercises that will challenge students to excel, and working with students, either individually or in small groups, to clarify material whenever the need may arise.  
  It is this experience coupled with my abundant enthusiasm that I feel will make me an ideal candidate for this position.

  Please see my attached resume for a more comprehensive overview of my background and other qualifications.  
  Should you need any additional information, I can be reached by telephone at (802) 282-8205, or by e-mail at bfarman@cems.uvm.edu.  
  I am available for an interview or a discussion at your convenience.  
  Thank you for your time and consideration.  
  I look forward to hearing from you.

  \closing{Sincerely,}
  % \encl{Personal statement}
\end{letter}
\end{document}
