\documentclass{letter}
\openup 5pt
\pdfpageheight 11in
\usepackage[margin=1in]{geometry}
\signature{Blake Farman}
\address{13B Franklin Street\\Winooski, VT 05404}
\begin{document}

\newcommand{\posting}{Entry Level Software Engineer}
\newcommand{\loc}{Monster.com}
\newcommand{\employer}{Amazon}

\begin{letter}{\employer}
  \opening{To whom it may concern:}
  
  I am writing to you with regard to the \posting posting on \loc.  
  I have recently graduated from the University of Vermont with an M.S. in Mathematics and also hold a B.S. in Computer Science from Rensselaer Polytechnic Institute.
  % I am a recent graduate from Rensselaer Polytechnic Institute, where I received a Bachelor of Science degree in Computer Science, and will be embarking upon a Master of Sciece degree program at the University of Vermont this fall.
  I am currently seeking full time employment and I believe I possess a unique skill set that will allow me to make a valuable contribution to any development team.

  I have educational and academic research experience with C/C++, primarily in a Unix/Linux environment, as well as some real world development and an extensive accompanying mathematical background.
  Additionally, I am quite capable of learning new languages quickly.
  I am a highly motivated individual with a strong interest in software design and a desire to continue to grow my experience through real world problem solving.  
  I believe my eagerness to learn along with my academic and practical experience will make me an ideal candidate for this position.

  Please see my attached resume for a more comprehensive overview of my background and other qualifications.  
  Should you need any additional information, I can be reached by telephone at (802) 282-8205, or by e-mail at farmanb@gmail.com.  
  I am available for an interview or a discussion at your convenience.  
  
  Thank you for your consideration.  
  I look forward to hearing from you.
  
  % I will be graduating this May from the University of Vermont with a master of science degree in mathematics and I am currently seeking employment in the field of education.  
  % I am very interested in this position and I believe my skills and background will fit your needs.

  % I am a passionate and devoted student of mathematics.  
  % Indeed, I hold the field in high esteem and I aspire to impart my appreciation of its inherent beauty.  
  % It is in part this aspiration that led me choose to attend the University of Vermont, where I was afforded the opportunity to independently teach a total of five undergraduate level mathematics courses in introductory discrete mathematics and calculus.  
  % During this time I have found teaching to be an extremely rewarding endeavour and one which matches in equal measure the great fondness I hold for my own studies.  
  % I have acquired significant experience in preparing and delivering lectures, crafting exercises that will challenge students to excel, and working with students, either individually or in small groups, to clarify material whenever the need may arise.  
  % It is this experience coupled with my abundant enthusiasm that I feel will make me an ideal candidate for this position.

  % Please see my attached resume for a more comprehensive overview of my background and other qualifications.  
  % Should you need any additional information, I can be reached by telephone at (802) 282-8205, or by e-mail at bfarman@cems.uvm.edu.  
  % I am available for an interview or a discussion at your convenience.  
  % Thank you for your time and consideration.  
  % I look forward to hearing from you.

  \closing{Sincerely,}
  % \encl{Personal statement}
\end{letter}
\end{document}
